---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dsci310.assign5

<!-- badges: start -->
<!-- badges: end -->

The goal of dsci310.assign5 is to follow along the toy demo in [jennybc/regexcite](https://github.com/jennybc/regexcite). 
This package makes regular expressions more exciting. It provides convenience functions to make some common string manupulation tasks easier.


## Installation

You can install the development version of dsci310.assign5 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("samnthorne/dsci-310-assign5")
```

## Example

This is a basic example which shows you how to solve the common problem of splitting strings into character vectors:

```{r example}
library(dsci310.assign5)

(x <- "i,am,beautiful")
str_split_one(x, pattern = ",")
```

Use `str_split_one()` when the input is known to be a single string.
For safety, it will error if its input has length greater than one.

`str_split_one()` is built on `stringr::str_split()`, so you can use its `n` argument and stringr's general interface for describing the `pattern` to be matched.

```{r}
str_split_one(x, pattern = ",", n = 2)

y <- "192.168.0.1"
str_split_one(y, pattern = stringr::fixed("."))
```
